### 2013-10-30 Paper/introduction.tex
writing case study

*** TODO: Introduction to expert retrieval and learn to rank goes here ***

The designed framework can be categorized in domain of on-line translation. The framework aims to find the best translator-corrector combination for a client who seeks for a reasonable offer to translate a document.

The profile of every translator consists of different aspects like offered price per word, translation time per word, experience and quality of translation in a specific language pair (source and destination languages). Based on client's document, the system figures out the value of each aspect and offers the first three most related translators. As it is clear, the aspects are in different scales (price in currency, time in minute and etc.). It should also mentioned that the one with best offer in all aspects (lowest price, fastest time, most similar to previous experience and etc.) may not be the best offer and leads to a low quality translation and unsatisfied client.

In order to evaluate the quality of translators and also whole the task, a feedback system for corrector and client is considered. After finishing translator's task, the corrector starts revising the text and leaving a feedback on it. The feedback of corrector which is a number between one to five is used as a base for estimating the proficiency of translator. Then by delivering the task to the client, his feedback is asked. The feedback of client is used to deploy and leverage ranking system.

In Section II, the designed Translator-Expert Retrieval framework is discussed in detail. Then, Section III summarizes system evolution and achieved results. Finally conclusion is written down in section IV.

>>>>

*** TODO: Introduction ***

% The designed framework can be categorized in domain of on-line translation. The framework aims to find the best translator-corrector % combination for a client who seeks for a reasonable offer to translate a document.

% The profile of every translator consists of different aspects like offered price per word, translation time per word, experience and  quality of translation in a specific language pair (source and destination languages). Based on client's document, the system figures out the value of each aspect and offers the first three most related translators. As it is clear, the aspects are in different scales (price in currency, time in minute and etc.). It should also mentioned that the one with best offer in all aspects (lowest price, fastest time, most %similar to previous experience and etc.) may not be the best offer and leads to a low quality translation and unsatisfied client.

% In order to evaluate the quality of translators and also whole the task, a feedback system for corrector and client is considered. After finishing translator's task, the corrector starts revising the text and leaving a feedback on it. The feedback of corrector which is a number between one to five is used as a base for estimating the proficiency of translator. Then by delivering the task to the client, his feedback is asked. The feedback of client is used to deploy and leverage ranking system.

% In Section II, the designed Translator-Expert Retrieval framework is discussed in detail. Then, Section III summarizes system evolution and achieved results. Finally conclusion is written down in section IV.
